---
title: "Maplewood"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme:
      version: 4
      bootswatch: minty
      base_font: 
        google: Prompt
      heading_font:
        google: Sen
      code_font:
        google: 
          # arguments to sass::font_google() 
          family: JetBrains Mono
          local: false
  
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(highcharter) 
library(billboarder)
library(gt)
library(htmltools)
library(viridis)
library(xfun)
library(shiny)
library(RColorBrewer)
```

```{r}
pums <- read_csv("pums_recs_matched_v1.csv")

```

Building Characteristics
======================================================================
Column {.sidebar data-width=250}
----------------------------------------------------------------------
```{r}
sliderInput("income", "Annual Gross Household Income", min = 0, max = 500000, value = c(0,500000))

pums_filter_on_income <- reactive({pums %>%
  filter(FINCP >= input$income[1] & FINCP <= input$income[2])}) 

pums_min_income <- reactive({
  min(pums_filter_on_income()$FINCP)
})

pums_max_income <- reactive({
  max(pums_filter_on_income()$FINCP)
})
#renderPrint(pums_min_income())
#renderPrint(pums_max_income())
```

Column {.tabset .tabset-fade data-width=750}
-----------------------------------------------------------------------
### Heating Equipment
```{r}
pums$EQUIPM<- factor(pums$EQUIPM,
                 levels = c(2,3,4,5,6,7,8,9,10,21,-2),
                 labels = c("Steam/hot water system with radiators or pipes", "Central furnace", "Heat pump", "Built-in electric units installed in walls, ceilings, baseboards, or floors", "Built-in floor/wall pipeless furnace", "Built-in room heater burning gas, oil, or kerosene", "Wood-burning stove (cordwood or pellets)", "Fireplace", "Portable electric heaters", "Some other equipment", NA))

pums$EQUIPAGE<- factor(pums$EQUIPAGE,
                 levels = c(1,2,3,41,42,5,-2),
                 labels = c("Less than 2 years old", "2 to 4 years old", "5 to 9 years old", "10 to 14 years old", "15 to 19 years old", "20 years or older", NA))


#table(pums$AGECENAC)
#table(pums$COOLTYPE)

heat_equip_reactive = reactive({
  pums %>%
    filter(EQUIPM %in% c("Steam/hot water system with radiators or pipes", "Central furnace", "Heat pump"),
           EQUIPAGE %in% c("Less than 2 years old", "2 to 4 years old", "5 to 9 years old", "10 to 14 years old", "15 to 19 years old", "20 years or older"),
           (FINCP >= pums_min_income() & FINCP <= pums_max_income())) %>%
  group_by(EQUIPAGE, EQUIPM) %>%
  summarise(CNT = n())})

#View(y)

#renderPrint(y_reactive())
```

```{r}
renderHighchart(hchart(heat_equip_reactive(), type = 'column', hcaes(x = EQUIPAGE, y = CNT, group = EQUIPM)) |>
    hc_xAxis(
     title = list(text = "Age of Heating Equipment")
    ) |>
   hc_yAxis(
    title = list(text = " ")
    ) |>
   hc_title(
    style = list(color = hex_to_rgba("black", 0.5)),
    text = "Main Space Heating Equipment Type"
    )
)



```
### Cooling Equipment
```{r}
pums$COOLTYPE<- factor(pums$COOLTYPE,
                 levels = c(1,2,3,-2),
                 labels = c("Central air conditioning system", "Individual window wall or portable units", "Both a central system and individual units", NA))

pums$AGECENAC<- factor(pums$AGECENAC,
                 levels = c(1,2,3,41,42,5,-2),
                 labels = c("Less than 2 years old", "2 to 4 years old", "5 to 9 years old", "10 to 14 years old", "15 to 19 years old", "20 years or older", NA))

#table(pums$AGECENAC)
#table(pums$COOLTYPE)
cool_equip_reactive = reactive({pums %>%
  filter(COOLTYPE %in% c("Central air conditioning system", "Individual window wall or portable units", "Both a central system and individual units"), AGECENAC %in% c("Less than 2 years old", "2 to 4 years old", "5 to 9 years old", "10 to 14 years old", "15 to 19 years old", "20 years or older"),
         (FINCP >= pums_min_income() & FINCP <= pums_max_income())) %>%
  group_by(AGECENAC, COOLTYPE) %>%
  summarise(CNT = n())})

```

```{r}

#Create highchart
renderHighchart(hchart(cool_equip_reactive(), type = 'column', hcaes(x = AGECENAC, y = CNT, group = COOLTYPE)) |>
   hc_chart(
    #backgroundColor = "black"
    backgroundColor = hex_to_rgba("lightgrey", 0.5)
    ) |>
   hc_xAxis(
    title = list(text = "Age of Cooling Equipment")
    ) |>
   hc_yAxis(
    title = list(text = " ")
    ) |>
   hc_title(
    style = list(color = hex_to_rgba("black", 0.5)),
    text = "Type of Air Conditioning Equipment Used"
    )
)

```

### Other Equipment
```{r}

pums_other_equip <- pums %>%
  select(AGEDW, AGECWASH, AGERFRI1, AGEFRZR, AGECDRYER,FINCP)
#glimpse(pums_other_equip)

pums_other_equip_long <- pums_other_equip %>%
  pivot_longer(cols = c("AGEDW", "AGECWASH", "AGERFRI1", "AGEFRZR", "AGECDRYER"),
               names_to = "Other_Equipment",
               values_to = "Other_Equipment_Age")


pums_other_equip_long$Other_Equipment_Age <- factor(pums_other_equip_long$Other_Equipment_Age,
                                                    levels = c(1,2,3,41,42,5,-2),
                 labels = c("Less than 2 years old", "2 to 4 years old", "5 to 9 years old", "10 to 14 years old", "15 to 19 years old", "20 years or older", NA))



pums_other_equip_long$Other_Equipment <- factor(pums_other_equip_long$Other_Equipment,
                                                levels = c("AGEDW", "AGECWASH", "AGERFRI1", "AGEFRZR", "AGECDRYER"),
                                                labels = c("Dishwasher", "Clothes Washer", "Refrigerator", "Freezer", "Dryer"))
#View(pums_other_equip_long)


other_equip_reactive = reactive({ pums_other_equip_long %>%
  filter(Other_Equipment %in% c("Dishwasher", "Clothes Washer", "Refrigerator", "Freezer", "Dryer"), Other_Equipment_Age %in% c("Less than 2 years old", "2 to 4 years old", "5 to 9 years old", "10 to 14 years old", "15 to 19 years old", "20 years or older"),
         (FINCP >= pums_min_income() & FINCP <= pums_max_income())) %>%
  group_by(Other_Equipment_Age, Other_Equipment) %>%
  summarise(CNT = n())
})
#View(y)
```


```{r}
renderHighchart(hchart(other_equip_reactive(), type = 'column', hcaes(x = Other_Equipment_Age, y = CNT, group = Other_Equipment)) |>
   hc_xAxis(
    title = list(text = "Age of Other Equipment")
    ) |>
   hc_yAxis(
    title = list(text = " ")
    ) |>
   hc_title(
    style = list(color = hex_to_rgba("black", 0.5)),
    text = "Other Equipment Type"
    )
)

```

### Lightbulbs

```{r}

pums$LGTINNUM <- factor(pums$LGTINNUM,
                        levels = c(1,2,3,4,5),
                        labels = c("Fewer than 20 light bulbs", "20 to 39 light bulbs", "40 to 59 light bulbs", "60 to 79 light bulbs", "80 or more light bulbs"))
#View(pums)
```


```{r}
lightbulbs_reactive = reactive({ pums %>%
  filter(LGTINNUM %in% c("Fewer than 20 light bulbs", "20 to 39 light bulbs", "40 to 59 light bulbs", "60 to 79 light bulbs", "80 or more light bulbs"),
         (FINCP >= pums_min_income() & FINCP <= pums_max_income())) %>%
  group_by(LGTINNUM) %>%
  summarise(CNT = n())
})
#table(y)

```

```{r}

bulbs_inside <-renderHighchart(hchart(lightbulbs_reactive(), "pie", hcaes(x = LGTINNUM, y = CNT)) %>%
  hc_title(text = "Number of light bulbs installed inside the home") %>%
  #hc_add_theme(hc_theme_ggplot2())
#hc_add_theme(hc_theme_google())
  #hc_add_theme(hc_theme_bloom())
  hc_add_theme(hc_theme_ffx()))
```
 

```{r}

pums$LGTOUTNUM <- factor(pums$LGTOUTNUM,
                        levels = c(0,1,2,3,-2),
                        labels = c("None", "1 to 4 bulbs", "5 to 9 bulbs", "10 or more bulbs", NA))

```

```{r}
lightbulbs_reactive_outside = reactive({ pums %>%
  filter(LGTOUTNUM %in% c("None", "1 to 4 bulbs", "5 to 9 bulbs", "10 or more bulbs"),
         (FINCP >= pums_min_income() & FINCP <= pums_max_income())) %>%
  group_by(LGTOUTNUM) %>%
  summarise(CNT = n())
  
})
#table(y)

```

```{r}

bulbs_outside <-renderHighchart(hchart(lightbulbs_reactive_outside(), "pie", hcaes(x = LGTOUTNUM, y = CNT)) %>%
  hc_title(text = "Number of light bulbs installed outside the home") %>%
  #hc_add_theme(hc_theme_ggplot2())
#hc_add_theme(hc_theme_google())
  #hc_add_theme(hc_theme_bloom())
  hc_add_theme(hc_theme_ffx()))
```

```{r}
splitLayout(cellWidths = c("50%"), bulbs_inside, bulbs_outside)
``` 


Energy Consumption Baseline
======================================================================
Column {.sidebar data-width=250}
----------------------------------------------------------------------
```{r}
sliderInput("hhincome", "Annual Gross Household Income", min = 0, max = 500000, value = c(0,500000))

pums_filter_on_hhincome <- reactive({pums %>%
  filter(FINCP >= input$hhincome[1] & FINCP <= input$hhincome[2])}) 

pums_min_hhincome <- reactive({
  min(pums_filter_on_hhincome()$FINCP)
})

pums_max_hhincome <- reactive({
  max(pums_filter_on_hhincome()$FINCP)
})
#renderPrint(pums_min_hhincome())
#renderPrint(pums_max_hhincome())
```

Column {.tabset .tabset-fade data-width=750}
-----------------------------------------------------------------------

### Main Space Heating

```{r}
pums$FUELHEAT <- factor(pums$FUELHEAT,
                        levels = c(1,2,3,5,7,21,-2),
                        labels = c("Natural gas", "Propane", "Fuel oil/kerosene", "Electricity", "Wood", "Some other fuel", NA))
#table(pums$FUELHEAT)
```

```{r}
main_space_fuel <- reactive({pums %>%
  filter(FUELHEAT %in% c("Natural gas", "Propane", "Fuel oil/kerosene", "Electricity", "Wood", "Some other fuel"),
         (FINCP >= pums_min_hhincome() & FINCP <= pums_max_hhincome())) %>%
  group_by(FUELHEAT) %>%
  summarise(CNT = n())
})
#table(y)

```

```{r}
cols <- viridis(8)
#custom_colors <- viridis::mako(n = 15)
renderHighchart(hchart(main_space_fuel(), "pie", hcaes(x = FUELHEAT, y = CNT)) %>%
                  hc_title(text = "Main space Heating Fuel") %>%
                  hc_colors(cols) %>%
                  #hc_add_theme(hc_theme_ggplot2())
                  #hc_add_theme(hc_theme_google())
                  #hc_add_theme(hc_theme_bloom())
                  hc_add_theme(hc_theme_ffx()))
```

### Main Water Heater
```{r}
pums$FUELH2O <- factor(pums$FUELH2O,
                       levels = c(1,2,3,5,7,8,21),
                       labels = c("Natural gas", "Propane", "Fuel oil/kerosene", "Electricity", "Wood", "Solar", "Some other fuel"))
```


```{r}
cols <- viridis(8)
#cols <- substr(cols, 0, 10)
main_water_heater_fuel <- reactive({pums %>%
   filter(FUELH2O %in% c("Natural gas", "Propane", "Fuel oil/kerosene", "Electricity", "Wood", "Solar", "Some other fuel"),
         (FINCP >= pums_min_hhincome() & FINCP <= pums_max_hhincome())) %>%
   group_by(FUELH2O) %>%
   summarise(CNT = n())
})
#table(y)
 
renderHighchart(hchart(main_water_heater_fuel(), "pie", hcaes(x = FUELH2O, y = CNT)) %>%
  hc_title(text = "Fuel Used by Main Water Heater") %>%
hc_add_theme(hc_theme_ffx()))

```

### Stove
```{r}
pums$STOVENFUEL <- factor(pums$STOVENFUEL,
                       levels = c(1,2,5,13,21,-2),
                       labels = c("Natural gas", "Propane", "Electricity", "Dual fuel", "Some other fuel", NA))
```

```{r}
cols <- viridis(8)
#cols <- substr(cols, 0, 10)
stove_fuel <- reactive({pums %>%
   filter(STOVENFUEL %in% c("Natural gas", "Propane", "Electricity", "Dual fuel", "Some other fuel"),
         (FINCP >= pums_min_hhincome() & FINCP <= pums_max_hhincome())) %>%
   group_by(STOVENFUEL) %>%
   summarise(CNT = n())
})
 
renderHighchart(hchart(stove_fuel(), "pie", hcaes(x = STOVENFUEL, y = CNT)) %>%
  hc_title(text = "Fuel used by stove") %>%
hc_add_theme(hc_theme_ffx()))
```

### Clothes Dryer
```{r}
pums$DRYRFUEL <- factor(pums$DRYRFUEL,
                       levels = c(1,2,5,-2),
                       labels = c("Natural gas", "Propane", "Electricity", NA))
```

```{r}
cols <- viridis(8)
#cols <- substr(cols, 0, 10)
dryer_fuel <- reactive({pums %>%
   filter(DRYRFUEL %in% c("Natural gas", "Propane", "Electricity"),
         (FINCP >= pums_min_hhincome() & FINCP <= pums_max_hhincome())) %>%
   group_by(DRYRFUEL) %>%
   summarise(CNT = n())
})
 
renderHighchart(hchart(dryer_fuel(), "pie", hcaes(x = DRYRFUEL, y = CNT)) %>%
  hc_title(text = " Fuel used by clothes dryer") %>%
hc_add_theme(hc_theme_ffx()))
```

Technology Adoption
======================================================================
Column {.sidebar data-width=250}
----------------------------------------------------------------------
```{r}
sliderInput("hhaincome", "Annual Gross Household Income", min = 0, max = 500000, value = c(0,500000))

pums_filter_on_hhaincome <- reactive({pums %>%
  filter(FINCP >= input$hhaincome[1] & FINCP <= input$hhaincome[2])}) 

pums_min_hhaincome <- reactive({
  min(pums_filter_on_hhaincome()$FINCP)
})

pums_max_hhaincome <- reactive({
  max(pums_filter_on_hhaincome()$FINCP)
})
renderPrint(pums_min_hhaincome())
renderPrint(pums_max_hhaincome())
```
Column {data-width=200}
----------------------------------------------------------------------
### Using Solar
```{r}
pums_solar<-pums %>%
    count(USESOLAR) %>%
    # count creates a column called 'n'
    mutate(percent = n / sum(n) * 100)

valueBox(scales::percent((100 - pums_solar$percent)/100), icon = "fa-thumbs-down",col="orange")
```

Column {data-width=200}
-----------------------------------------------------------------------
### Smart Thermostat
```{r}
pums_SMARTTHERM<-pums %>%
    count(SMARTTHERM) %>%
    # count creates a column called 'n'
    mutate(percent = n / sum(n) * 100)

pums_SMARTTHERM_yes <- pums_SMARTTHERM %>%
  filter(SMARTTHERM == 1)

valueBox(scales::percent((pums_SMARTTHERM_yes$percent)/100), icon = "fa-line-chart",col="lightgreen")
```

Column {data-width=200}
-----------------------------------------------------------------------
### Electricity Smart Meter
```{r}
pums_SMARTMETER<-pums %>%
    count(SMARTMETER) %>%
    # count creates a column called 'n'
    mutate(percent = n / sum(n) * 100)

pums_SMARTMETER_yes <- pums_SMARTMETER %>%
  filter(SMARTMETER == 1)

valueBox(scales::percent((pums_SMARTMETER_yes$percent)/100), icon = "fa-line-chart",col = "lightblue")
```

Column {data-width=400}
-----------------------------------------------------------------------
### {.no-padding}
```{r}
#Outside light bulb motion detector
y = pums %>%  
  group_by(LGTOUTCNTL) %>% 
  summarise(CNT = n())

#Donut Chart
billboarder() %>% 
  bb_donutchart(y) %>% 
  bb_legend(position = 'right') %>%
  bb_data(names = list("1" = "Yes", "0" = "No", "-2" = "Not applicable"), labels = TRUE) %>%
  bb_title("Outside light bulbs controlled by motion detectors or light sensors") %>%
  bb_color(palette = RColorBrewer::brewer.pal(5,"Set2"))


```

### {.no-padding}
```{r}
#Portion of inside light bulbs that are LED
y = pums %>%  
  group_by(LGTINLED) %>% 
  summarise(CNT = n())

#Donut Chart
billboarder() %>% 
  bb_donutchart(y) %>% 
  bb_legend(position = 'right') %>%
  bb_data(names = list("1" = "All", "2" = "Most", "3" = "About half", "4" = "Some", "0" = "None"), labels = TRUE) %>%
  bb_title("Portion of inside light bulbs that are LED") %>%
  bb_color(palette = RColorBrewer::brewer.pal(5,"Set2"))

```





Demographic Information
======================================================================

Column {.tabset .tabset-fade data-width=650}
-----------------------------------------------------------------------

### Income

```{r}

pums$MONEYPY <- factor(pums$MONEYPY,
                        levels = c(1,2,3,4,5,6,7,8),
                        labels = c("< $20,000", "$20,000 - $39,999", "$40,000 - $59,999", "$60,000 - $79,999", "$80,000 - $99,999", "$100,000 - $119,999", "$120,000 - $139,999", ">= $140,000"))


pums$HOUSEHOLDER_RACE <- factor(pums$HOUSEHOLDER_RACE,
                                levels = c(1,2,3,4,5,6,7),
                                labels = c("White", "Black or African/American", "American Indian or Alaska Native", "Asian", "Native Hawaiian or Other Pacific Islander", "Some Other Race", "2 or More Races"))

y = pums %>%
  filter(HOUSEHOLDER_RACE %in% c("White", "Black or African/American","Asian", "2 or More Races"), MONEYPY %in% c("< $20,000", "$20,000 - $39,999", "$40,000 - $59,999", "$60,000 - $79,999", "$80,000 - $99,999", "$100,000 - $119,999", "$120,000 - $139,999", ">= $140,000")) %>%
  group_by(MONEYPY, HOUSEHOLDER_RACE) %>%
  summarise(CNT = n())

#table(y)

#Create highchart
hchart(y, type = 'column', hcaes(x = MONEYPY, y = CNT, group = HOUSEHOLDER_RACE)) |>
   hc_xAxis(
    title = list(text = "Income")
    ) |>
   hc_yAxis(
    title = list(text = " ")
    ) |>
   hc_title(
    style = list(color = hex_to_rgba("black", 0.5), fontSize = "25px", fontWeight = "bold"),
    text = "Annual Gross Household Income by Race"
    )

```


### Age

```{r}

# Colors
custom_colors <- viridis::mako(n = 15)

hchart(
  pums$HHAGE, 
  color = "#5D69B1", name = "Age"
  )%>%
  hc_add_theme(hc_theme_google()) %>%
  hc_tooltip(pointFormat = "<b>Age: </b> {point.y} <b>")%>%
  hc_title(text = "Distribution of Respondent's Age", 
           style = list(color = hex_to_rgba("black", 0.5),fontSize = "25px", fontWeight = "bold")) %>%
  hc_credits(enabled = TRUE)

```
Column {data-width=350}
-----------------------------------------------------------------------

### {.no-padding}

```{r}
cols <- viridis(8)
#cols <- substr(cols, 0, 10)
 y = pums %>%
   filter(MONEYPY %in% c("< $20,000", "$20,000 - $39,999", "$40,000 - $59,999", "$60,000 - $79,999", "$80,000 - $99,999", "$100,000 - $119,999", "$120,000 - $139,999", ">= $140,000")) %>%
   group_by(MONEYPY) %>%
   summarise(CNT = n())

hchart(y, "pie", hcaes(x = MONEYPY, y = CNT)) %>%
   hc_title(text = "Annual Gross Household Income for the Last Year",
            style = list(fontSize = "14px", fontWeight = "bold")) %>%
  hc_add_theme(hc_theme_ffx()) %>%
  hc_colors(cols)
```

### {.no-padding}
```{r}
cols <- viridis(4)

y = pums %>%
  filter(HOUSEHOLDER_RACE %in% c("White", "Black or African/American","Asian", "2 or More Races")) %>%
  group_by(HOUSEHOLDER_RACE) %>%
  summarise(CNT = n())

hchart(y, "pie", hcaes(x = HOUSEHOLDER_RACE, y = CNT)) %>%
   hc_title(text = "Householder Race",
            style = list(fontSize = "14px", fontWeight = "bold")) %>%
  hc_add_theme(hc_theme_ffx()) %>%
  hc_colors(cols)

```


